---
title: Additional Tools for glmnet
output:
    rmarkdown::html_vignette:
        toc_float: true
vignette: >
    %\VignetteIndexEntry{Additional Tools for glmnet}
    %\VignetteEngine{knitr::rmarkdown}
    %\VignetteEncoding{UTF-8}
bibliography: bibliography.bib
---

# Introduction

The `glmnettools` package offers functions for repeated cross-validation and
prediction of survival probabilities using the `glmnet` package
[@friedman2010; @simon2011].

# Repeated Cross-Validation

The example is taken from the `cv.glmnet` manual page (`?"glmnet::cv.glmnet"`):

```{r exampledata}
library("glmnettools")

# Generating example data
set.seed(1010)
n <- 1000
p <- 100
nzc <- trunc(p/10)
x <- matrix(rnorm(n * p), n, p)
beta <- rnorm(nzc)
fx <- x[, seq(nzc)] %*% beta
eps <- rnorm(n) * 5
y <- drop(fx + eps)
```

```{r rcvglmnet}
set.seed(1011)
# nrepcv should usually be higher but to keep the runtime of the example low
# we choose 2 here, same for the nfolds
rcvob <- rcv.glmnet(x, y, nrepcv = 2, nfolds = 3)
plot(rcvob)
title("Gaussian Family", line = 2.5)
coef(rcvob)
predict(rcvob, newx = x[1:5, ], s = "lambda.min")
```

# Prediction Survival Probabilities

The example is taken from the `cv.glmnet` manual page (`?"glmnet::cv.glmnet"`):

```{r survexampledata}
library("survival")

set.seed(10101)
n <- 500
p <- 30
nzc <- trunc(p / 10)
x <- matrix(rnorm(n * p), n, p)
beta <- rnorm(nzc)
fx <- x[, seq(nzc)] %*% beta / 3
hx <- exp(fx)
ty <- rexp(n, hx)
tcens <- rbinom(n = n, prob = 0.3, size = 1)  # censoring indicator
y <- Surv(ty, 1 - tcens)

rcvob <- rcv.glmnet(x, y, family = "cox", nrepcv = 2, nfolds = 3)

## predicting survival probabilities
predict(
    rcvob,
    newx = x[1:5,], x = x, y = y,
    type = "survival", times = c(0, 7), s = "lambda.1se"
)

## linear predictor
predict(rcvob, newx = x[1:5,], type = "link", s = "lambda.1se")
```

# Session information
```{r si}
sessionInfo()
```

# References
